---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# natmanager

<!-- badges: start -->
[![natmanager](https://img.shields.io/badge/natmanager-Part%20of%20the%20natverse-a241b6)](https://natverse.github.io)
[![Docs](https://img.shields.io/badge/docs-100%25-brightgreen.svg)](https://natverse.github.io/natmanager/reference/)
[![Travis build status](https://travis-ci.org/natverse/natmanager.svg?branch=master)](https://travis-ci.org/natverse/natmanager)
<!-- badges: end -->

The goal of natmanager is to handle the installation of all packages inside the natverse repository.

# Prerequisite
To install this package you need to have `R` and `RStudio` installed. The detailed instructions per operating system are given below. Further you would also need a valid GitHub account to install packages inside the natverse repository, see  [Usage](#usage)

### Linux
1. Install `r`, in terminal type below:
```{r, engine = 'bash', eval = FALSE}
sudo apt-get install libopenblas-base r-base
```



2. Install `RStudio`, in terminal type below:
```{r, engine = 'bash', eval = FALSE}
sudo apt-get install gdebi
cd ~/Downloads
wget https://download1.rstudio.org/rstudio-xenial-1.1.419-amd64.deb
sudo gdebi rstudio-xenial-1.1.419-amd64.deb
```


3. Start `RStudio`, in terminal type below:
```{r, engine = 'bash', eval = FALSE}
rstudio
```

### Mac OS X
1. Install `r` from here:
[r-installation](http://cloud.r-project.org/bin/macosx/)


2. Install `RStudio`, from here:
[RStudio-installation](https://rstudio.com/products/rstudio/download/#download)


3. Start `RStudio` from Launchpad

### Windows
1. Install `r` from here:
[r-installation](http://cloud.r-project.org/bin/windows/base/)


2. Install `RStudio`, for Windows from here:
[RStudio-installation](https://rstudio.com/products/rstudio/download/#download)


3. Start `RStudio` from Programs menu


# Installation

You can install the released version of natmanager from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("natmanager")
```

Or the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("natverse/natmanager")
```


# Usage {#usage}

Once installed, you can load/attach the package as follows:

```r
library('natmanager')
```

Further, you can install packages inside the natverse repository as follows:

```r
install('natverse')
```

You can also look at all the repos available in the natverse organization as follows:

```r
list_repo()
```

# FAQs

1. On using `install` function from the package to install a `natverse` repository, 
   I'm getting an error like below:
```r
Error: (converted from warning) package 'xx' was built under R version y.y.y
Execution halted
ERROR: lazy loading failed for package 'xx' 
```
This occurs mainly when your `r` version is lower than what the package was built for (mainly `CRAN` packages are built 
with latest version). If you are sure that it is a problem due to version, then you use like below and retry the `install` function.
```r
Sys.setenv("R_REMOTES_NO_ERRORS_FROM_WARNINGS"=TRUE)
```
See further discussion [here](https://github.com/r-lib/remotes/issues/403)


