---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# natmanager

<!-- badges: start -->
[![natmanager](https://img.shields.io/badge/natmanager-Part%20of%20the%20natverse-a241b6)](https://natverse.github.io)
[![Docs](https://img.shields.io/badge/docs-100%25-brightgreen.svg)](https://natverse.github.io/natmanager/reference/)
[![Travis build status](https://travis-ci.org/natverse/natmanager.svg?branch=master)](https://travis-ci.org/natverse/natmanager)
<!-- badges: end -->

The goal of natmanager is to handle the installation of all packages inside the natverse repository.

## Installation

You can install the released version of natmanager from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("natmanager")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("natverse/natmanager")
```
Once installed, you can install packages inside the natverse repository as follows:

```r
natmanager::install('natverse')
```

You can also look at all the repos avaiable in the natverse organization as follows:

```{r list repos}
natmanager::list_repo()
```

